# 1. Data processing

Load data and fill out some variables.
```{r}
roh <- read.csv2("C:/Users/sylvi/Documents/0. Arbeit/Studium/Bachelorarbeit/Rohdaten/SV044 qPCR SBNO1 stability KO.csv",sep=";", dec=".")

data <- roh[, c("Well.Position", "Sample.Name", "Target.Name", "CT")]
#View(data)

nmbr_of_samples = 11 #including control (control/NTC should be last)
nmbr_of_targets = 2 #including housekeeper, colors in qqplot chunk need to be adjusted!
nmbr_of_replicates = 3
name_housekeeper = "SRSF4"
name_normalize = "ctrl I" # name of the sample you want to use for normalization
name_normalize2 = "ctrl II"# name of a second sample you want to use for normalization
targets_norm2 <- c("ctrl II", "TRIM33 II", "TRIM28 II", "MIB1 II", "USP28 II", "ctrl II")

#it happened before that CT-values from the csv data were not imported as numbers, but characters. If this is the case the following steps are required. Make sure that the decimal is written with a "." not ",". 

data[,"CT"] <- as.numeric(data[,"CT"])

```

Separate the targets 
```{r}
targets = list()
for (i in c(1:nmbr_of_targets)){
  targets[[i]] = data[((i-1)*nmbr_of_replicates*nmbr_of_samples + 1):(i*nmbr_of_replicates*nmbr_of_samples), ]
  names(targets)[[i]] <- targets[[i]][1, "Target.Name"]
}

```


Separate the samples. Create a List substructured > target > sample
```{r}
data_target_sample = list()
for (i in c(1:nmbr_of_targets)){
  data_target_sample[[i]] = list()
  target_name <- targets[[i]][1, "Target.Name"]
  
  for (s in c(1:nmbr_of_samples)){
    sample_data <- targets[[i]][((s-1)*nmbr_of_replicates + 1):(s*nmbr_of_replicates), ]
    sample_name <- sample_data[1, "Sample.Name"]
    data_target_sample[[i]][[sample_name]] <- targets[[i]][((s-1)*nmbr_of_replicates + 1):(s*nmbr_of_replicates), ]
  }
   names(data_target_sample)[i] <- target_name
}

```


Calculate the mean values and standard deviations for each sample of each target
```{r}
#mean
mean_values = list()
for (i in c(1:nmbr_of_targets)){
  mean_values[[i]] = list()
  target_name <- names(data_target_sample[i])
  for(s in c(1:nmbr_of_samples)){
    sample_name <- names(data_target_sample[[i]][s])
    mean_values[[i]][[sample_name]] <-  mean(data_target_sample[[i]][[s]]$CT, na.rm =TRUE)
  }
  names(mean_values)[i] <- target_name
}

#standard deviation
sd_values = list()
for (i in c(1:nmbr_of_targets)){
  sd_values[[i]] = list()
  target_name <- names(data_target_sample[i])
  for(s in c(1:nmbr_of_samples)){
    sample_name <- names(data_target_sample[[i]][s])
    sd_values[[i]][[sample_name]] <- sd(data_target_sample[[i]][[s]]$CT, na.rm =TRUE)
  }
  names(sd_values)[i] <- target_name
}

```


To cancel out replicates that do not fit the other two, we compare the sd to the difference between CT-mean and CT-value of the sample. If the difference between CT-mean and CT-value is higher than the standard deviation, the samples are excluded.
The mean and standard deviation are calculated again. Add the mean values and standard deviations to your List.

```{r}
#replicate removal
na_data_target_sample <- data_target_sample
for (i in c(1:nmbr_of_targets)){
  for (s in c(1:nmbr_of_samples)){
    for (t in c(1:3)){
      if (!is.na((data_target_sample[[i]][[s]][t,"CT"] - mean_values[[i]][[s]]) >= sd_values[[i]][[s]])){ 
        if (abs((data_target_sample[[i]][[s]][t,"CT"] - mean_values[[i]][[s]])) >= sd_values[[i]][[s]]){ # oder vlt schwellenwert der Abweichung besser -> nicht so viel Probenverlust
          na_data_target_sample[[i]][[s]][t,"CT"] <- NA
        }
      }
    }
  }
}


#mean calculation
nd_mean_values = list()
for (i in c(1:nmbr_of_targets)){
  nd_mean_values[[i]] = list()
  target_name <- names(na_data_target_sample[i])
  for(s in c(1:nmbr_of_samples)){
    sample_name <- names(na_data_target_sample[[i]][s])
    nd_mean_values[[i]][[sample_name]] <- mean(na_data_target_sample[[i]][[s]]$CT, na.rm =TRUE)
  }
  names(nd_mean_values)[i] <- target_name
}


#standard deviation calculation
nd_sd_values = list()
for (i in c(1:nmbr_of_targets)){
  nd_sd_values[[i]] = list()
  target_name <- names(na_data_target_sample[i])
  for(s in c(1:nmbr_of_samples)){
    sample_name <- names(na_data_target_sample[[i]][s])
    nd_sd_values[[i]][[sample_name]] <- sd(na_data_target_sample[[i]][[s]]$CT, na.rm =TRUE)
  }
  names(nd_sd_values)[i] <- target_name
}

```


Add the mean values and standard deviations to your List.

```{r}

#add mean values
na_data_target_sample_wm <- list()

for (i in c(1:nmbr_of_targets)){
  na_data_target_sample_wm[[i]] <- list()
  target_name <- names(na_data_target_sample[i])
  for(s in c(1:nmbr_of_samples)){
    means_merge <- data.frame(c(nd_mean_values[[i]][[s]], nd_mean_values[[i]][[s]], nd_mean_values[[i]][[s]]))
    names(means_merge) <- "mean"
    sample_name <- names(na_data_target_sample[[i]][s])
    na_data_target_sample_wm[[i]][[sample_name]] <- cbind(na_data_target_sample[[i]][[s]], means_merge)
  }
  names(na_data_target_sample_wm)[i] <- target_name
}


#add sd values
na_data_target_sample_wm_sd <- list()

for (i in c(1:nmbr_of_targets)){
  na_data_target_sample_wm_sd[[i]] <- list()
  target_name <- names(na_data_target_sample_wm[i])
  for(s in c(1:nmbr_of_samples)){
    sd_merge <- data.frame(c(nd_sd_values[[i]][[s]], nd_sd_values[[i]][[s]], nd_sd_values[[i]][[s]]))
    names(sd_merge) <- "standard deviation"
    sample_name <- names(na_data_target_sample_wm[[i]][s])
    na_data_target_sample_wm_sd[[i]][[sample_name]] <- cbind(na_data_target_sample_wm[[i]][[s]], sd_merge)
  }
  names(na_data_target_sample_wm_sd)[i] <- target_name
}

```


Select your housekeeper
```{r}
housekeeper <- na_data_target_sample_wm_sd[[name_housekeeper]]

```


Calculate Delta CT (subtract the housekeeper CT values from your measured values). From here on every step is repeated with the single replicate values for visualization later on. 
```{r}
data_m_dCT <- list()
for (i in c(1:nmbr_of_targets)){
  data_m_dCT[[i]] <- list()
  target_name <- names(na_data_target_sample_wm_sd[i])
  for (s in c(1:nmbr_of_samples)){
    sample_name <- names(na_data_target_sample_wm_sd[[i]][s])
    deltaCT <- na_data_target_sample_wm_sd[[i]][[s]]["mean"] - housekeeper[[s]]["mean"]
    names(deltaCT) <- "deltaCT"
    data_m_dCT[[i]][[sample_name]] <- cbind(na_data_target_sample_wm_sd[[i]][[s]], deltaCT)
  }
  names(data_m_dCT)[i] <- target_name
}

#single replicates
qPCR_sdat_dCT <- list()
for (i in c(1:nmbr_of_targets)){
  qPCR_sdat_dCT[[i]] <- list()
  target_name <- names(na_data_target_sample_wm_sd[i])
  for (s in c(1:nmbr_of_samples)){
    sample_name <- names(na_data_target_sample_wm_sd[[i]][s])
    deltaCT <- na_data_target_sample_wm_sd[[i]][[s]]["CT"] - housekeeper[[s]]["mean"]
    names(deltaCT) <- "deltaCT"
    qPCR_sdat_dCT[[i]][[sample_name]] <- cbind(na_data_target_sample_wm_sd[[i]][[s]], deltaCT)
  }
  names(qPCR_sdat_dCT)[i] <- target_name
}

```


To do Fehlerfortpflanzung, calculate SD (delta Ct). Like this: (SD(sample)^2 + SD(housekeeper)^2)^1/2. The sd values are not needed for single replicates. 
```{r}
data_m_dCT_sddCT <- list()
for (i in c(1:nmbr_of_targets)){
  data_m_dCT_sddCT[[i]] <- list()
  target_name <- names(data_m_dCT[i])
  for(s in c(1:nmbr_of_samples)){
    sample_name <- names(data_m_dCT[[i]][s])
    sd_deltaCT <- ((data_m_dCT[[i]][[s]]["standard deviation"])^2 + (housekeeper[[s]]["standard deviation"])^2)^(1/2)
    names(sd_deltaCT) <- "sd deltaCT"
    data_m_dCT_sddCT[[i]][[sample_name]] <- cbind(data_m_dCT[[i]][[s]], sd_deltaCT)
  }
  names(data_m_dCT_sddCT)[i] <- target_name
}

```


Normalize deltaCT over the chosen sample (see name_normalize) delta delta CT = dCT(sample) - dCT(normalization sample)

```{r}

data_m_dCT_sddCT_ddCT <- list()
for (i in c(1:nmbr_of_targets)){
  data_m_dCT_sddCT_ddCT[[i]] <- list()
  target_name <- names(data_m_dCT_sddCT[i])
  if (target_name %in% targets_norm2){
    for (s in c(1:nmbr_of_samples)){
      sample_name <- names(data_m_dCT_sddCT[[i]][s])
      delta_delta_CT <- data_m_dCT_sddCT[[i]][[s]]["deltaCT"] - data_m_dCT_sddCT[[i]][[name_normalize2]]["deltaCT"]
      names(delta_delta_CT) <- "delta deltaCT"
      data_m_dCT_sddCT_ddCT[[i]][[sample_name]] <- cbind(data_m_dCT_sddCT[[i]][[s]], delta_delta_CT)
    }} else {
      for (s in c(1:nmbr_of_samples)){
      sample_name <- names(data_m_dCT_sddCT[[i]][s])
      delta_delta_CT <- data_m_dCT_sddCT[[i]][[s]]["deltaCT"] - data_m_dCT_sddCT[[i]][[name_normalize]]["deltaCT"]
      names(delta_delta_CT) <- "delta deltaCT"
      data_m_dCT_sddCT_ddCT[[i]][[sample_name]] <- cbind(data_m_dCT_sddCT[[i]][[s]], delta_delta_CT)
    }}
  names(data_m_dCT_sddCT_ddCT)[i] <- target_name
}

#single replicates
qPCR_sdat_dCT_ddCT <- list()
for (i in c(1:nmbr_of_targets)){
  qPCR_sdat_dCT_ddCT[[i]] <- list()
  target_name <- names(qPCR_sdat_dCT[i])
  if (target_name %in% targets_norm2){
    for (s in c(1:nmbr_of_samples)){
      sample_name <- names(qPCR_sdat_dCT[[i]][s])
      delta_delta_CT <- qPCR_sdat_dCT[[i]][[s]]["deltaCT"] - data_m_dCT_sddCT[[i]][[name_normalize2]]["deltaCT"]
      names(delta_delta_CT) <- "delta deltaCT"
      qPCR_sdat_dCT_ddCT[[i]][[sample_name]] <- cbind(qPCR_sdat_dCT[[i]][[s]], delta_delta_CT)
    }} else {
      for (s in c(1:nmbr_of_samples)){
      sample_name <- names(qPCR_sdat_dCT[[i]][s])
      delta_delta_CT <- qPCR_sdat_dCT[[i]][[s]]["deltaCT"] - data_m_dCT_sddCT[[i]][[name_normalize]]["deltaCT"]
      names(delta_delta_CT) <- "delta deltaCT"
      qPCR_sdat_dCT_ddCT[[i]][[sample_name]] <- cbind(qPCR_sdat_dCT[[i]][[s]], delta_delta_CT)
    }}
  names(qPCR_sdat_dCT_ddCT)[i] <- target_name
}

```


Calculate the standard deviation of the delta delta CT SD(ddCT) = ((sddCT(Sample))^2 + (sddCT(deltaCT)))^2)^(1/2)
```{r}
data_m_dCT_sddCT_ddCT_sdddCT <- list()
for (i in c(1:nmbr_of_targets)){
  data_m_dCT_sddCT_ddCT_sdddCT[[i]] <- list()
  target_name <- names(data_m_dCT_sddCT_ddCT[i])
  if(target_name %in% targets_norm2){
    for (s in c(1:nmbr_of_samples)){
      sample_name <- names(data_m_dCT_sddCT_ddCT[[i]][s])
      sd_delta_delta_CT <- ((data_m_dCT_sddCT_ddCT[[i]][[s]]["sd deltaCT"])^2 + (data_m_dCT_sddCT_ddCT[[i]][[name_normalize2]]["sd deltaCT"])^2)^(1/2)
      names(sd_delta_delta_CT) <- "sd delta deltaCT"
      data_m_dCT_sddCT_ddCT_sdddCT[[i]][[sample_name]] <- cbind(data_m_dCT_sddCT_ddCT[[i]][[s]], sd_delta_delta_CT)
    }} else {
      for (s in c(1:nmbr_of_samples)){
      sample_name <- names(data_m_dCT_sddCT_ddCT[[i]][s])
      sd_delta_delta_CT <- ((data_m_dCT_sddCT_ddCT[[i]][[s]]["sd deltaCT"])^2 + (data_m_dCT_sddCT_ddCT[[i]][[name_normalize]]["sd deltaCT"])^2)^(1/2)
      names(sd_delta_delta_CT) <- "sd delta deltaCT"
      data_m_dCT_sddCT_ddCT_sdddCT[[i]][[sample_name]] <- cbind(data_m_dCT_sddCT_ddCT[[i]][[s]], sd_delta_delta_CT)
    }}
  names(data_m_dCT_sddCT_ddCT_sdddCT)[i] <- target_name
}
#View(data_m_dCT_sddCT_ddCT_sdddCT)
```

The 2^-ddCT values have to be calculated
```{r}
data_m_dCT_sddCT_ddCT_sdddCT_2ddCT <- list()
for (i in c(1:nmbr_of_targets)){
  data_m_dCT_sddCT_ddCT_sdddCT_2ddCT[[i]] <- list()
  target_name <- names(data_m_dCT_sddCT_ddCT_sdddCT[i])
  for (s in c(1:nmbr_of_samples)){
    sample_name <- names(data_m_dCT_sddCT_ddCT_sdddCT[[i]][s])
    twoddCT <- 2^(-data_m_dCT_sddCT_ddCT_sdddCT[[i]][[s]]["delta deltaCT"]) 
    names(twoddCT) <- "2^(delta deltaCT)"
    data_m_dCT_sddCT_ddCT_sdddCT_2ddCT[[i]][[sample_name]] <- cbind(data_m_dCT_sddCT_ddCT_sdddCT[[i]][[s]], twoddCT)
  }
  names(data_m_dCT_sddCT_ddCT_sdddCT_2ddCT)[i] <- target_name
}


#single replicates
qPCR_sdat_complete <- list()
for (i in c(1:nmbr_of_targets)){
  qPCR_sdat_complete[[i]] <- list()
  target_name <- names(qPCR_sdat_dCT_ddCT[i])
  for (s in c(1:nmbr_of_samples)){
    sample_name <- names(qPCR_sdat_dCT_ddCT[[i]][s])
    twoddCT <- 2^(-qPCR_sdat_dCT_ddCT[[i]][[s]]["delta deltaCT"]) 
    names(twoddCT) <- "2^(delta deltaCT)"
    qPCR_sdat_complete[[i]][[sample_name]] <- cbind(qPCR_sdat_dCT_ddCT[[i]][[s]], twoddCT)
  }
  names(qPCR_sdat_complete)[i] <- target_name
}

```


Last but not least: The standard deviation of 2^ddCT. SD(2ddCT) = ln(2) * 2^(-ddCT) * sdddCT
```{r}
data_complete <- list()
for (i in c(1:nmbr_of_targets)){
  data_complete[[i]] <- list()
  target_name <- names(data_m_dCT_sddCT_ddCT_sdddCT_2ddCT[i])
  for (s in c(1:nmbr_of_samples)){
    sample_name <- names(data_m_dCT_sddCT_ddCT_sdddCT_2ddCT[[i]][s])
    sdd2ddCT <- log(2)*2^(- data_m_dCT_sddCT_ddCT_sdddCT_2ddCT[[i]][[s]]["delta deltaCT"]) * data_m_dCT_sddCT_ddCT_sdddCT_2ddCT[[i]][[s]]["sd delta deltaCT"]
    names(sdd2ddCT) <- "sd 2^(delta deltaCT)"
    data_complete[[i]][[sample_name]] <- cbind(data_m_dCT_sddCT_ddCT_sdddCT_2ddCT[[i]][[s]], sdd2ddCT)
  }
  names(data_complete)[i] <- target_name
}

```


Display your beautiful data and be happy :)
```{r}
#View(data_complete)
#View(qPCR_sdat_complete)
```

We now want do portray the important data (2ddCT and sd 2ddCT) in a sensible way for plots. The control is left out
```{r}
qPCR_rel_data <- list()
target_names <- names(data_complete)

for (i in (1:nmbr_of_targets)){
  target_name <- target_names[[i]]
  
  target_2ddCT <- c()
  for (d in c(1:(nmbr_of_samples -1))){
    target_2ddCT <- c(target_2ddCT, data_complete[[target_name]][[d]]["2^(delta deltaCT)"][1,1])  
  }
  
  target_sdd2ddCT <- c()
  for (f in c(1:(nmbr_of_samples -1))){
    target_sdd2ddCT <- c(target_sdd2ddCT, data_complete[[target_name]][[f]]["sd 2^(delta deltaCT)"][1,1])  
  }
  
  qPCR_rel_data[[i]] <- data.frame(
    samples = names(data_complete[[target_name]])[-length(data_complete[[target_name]])],
    target_2ddCT = target_2ddCT,
    target_sdd2ddCT = target_sdd2ddCT
  )
  qPCR_rel_data[[i]]$samples <- factor(qPCR_rel_data[[i]]$samples, levels = names(data_complete[[target_name]])[-length(data_complete[[target_name]])])
  colnames(qPCR_rel_data[[i]]) <- c("samples", "2ddCT", "sd 2ddCT")
  
}
names(qPCR_rel_data) <- target_names

#View(qPCR_rel_data[["EGFP"]])
```

And we portray the single data 2ddCT values in a sensible data frame for dot-visualization
```{r}
qPCR_single_data <- list()
target_names <- names(qPCR_sdat_complete)

for (i in  c(1:(nmbr_of_targets))){
  target_name <- target_names[[i]]
  sampl_target_2ddCT <- c()
  for (d in c(1:(nmbr_of_samples -1))){
    sampl_target_2ddCT <- c(sampl_target_2ddCT, qPCR_sdat_complete[[target_name]][[d]]["2^(delta deltaCT)"][1:3,1])  
  }
    
  qPCR_single_data[[i]] <- data.frame(
    single_samples = rep(names(qPCR_sdat_complete[[target_name]])[-length(qPCR_sdat_complete[[target_name]])], each = 3),
    sample_2ddCT = sampl_target_2ddCT
    )
  qPCR_single_data[[i]]$single_samples <- factor(qPCR_single_data[[i]]$single_samples, 
                                          levels = names(qPCR_sdat_complete[[target_name]])[-length(qPCR_sdat_complete[[target_name]])])
  colnames(qPCR_single_data[[i]]) <- c("single_samples", "sample_2ddCT")
}
names(qPCR_single_data) <- target_names

#View(qPCR_single_data)
#View(qPCR_sdat_complete)
```



Now we make beautiful ggplots :)
These are the single replicates. The data points show the technical replicates.
```{r}
#install.packages("ggprism")
#install.packages("ggplot2")
library(ggplot2)
library(ggprism)

qPCR_bar_plots_stability <- list()
colors_fill <- c( "khaki1", "steelblue1")
colors_contour <- c( "goldenrod2", "steelblue4")

for (i in c(1:nmbr_of_targets)){
  target_2ddCT <- qPCR_rel_data[[i]][,"2ddCT"]
  target_sdd2ddCT <- qPCR_rel_data[[i]][,"sd 2ddCT"]
  single_samples <- qPCR_single_data[[i]][["single_samples"]]
  sample_2ddCT <- qPCR_single_data[[i]][["sample_2ddCT"]]
  
  qPCR_bar_plots_stability[[i]] <- ggplot()+
    geom_bar(data = qPCR_rel_data[[i]], aes(x = samples, y = target_2ddCT), stat = "identity", 
             fill = colors_fill[i], color = colors_contour[i], width = 0.6, size = 1)+
    geom_errorbar(data = qPCR_rel_data[[i]], aes(x = samples, ymin = target_2ddCT - target_sdd2ddCT, ymax = target_2ddCT + target_sdd2ddCT), 
                  color = colors_contour[i], width = 0.4, size = 0.8) +
    geom_point(data = qPCR_single_data[[i]], aes(x = single_samples, y = as.numeric(sample_2ddCT)), 
               position = position_jitter(width = 0.2), size = 3, color = colors_contour[i], na.rm = TRUE) +
    scale_x_discrete(labels = c("ctrl I", "ctrl II", 
                                "MIB1-KO I", "MIB-KO II", 
                                "TRIM28-KO I", "TRIM28-KO II", 
                                "TRIM33-KO I", "TRIM33-KO II",
                                "USP28-KO I", "USP28-KO II"))+
    #geom_text(data = qPCR_rel_data[[i]], aes(x = samples, y = target_2ddCT, label = round(target_2ddCT, 1)), vjust = -1) +
    theme_prism()+
    labs(y = expression(2^{Delta * Delta * CT}))+
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
  
  print(qPCR_bar_plots_stability[[i]])
} 

```



We now have to combine the replicates (mean, and sd). The data points will show the biological replicates.
```{r}
# Korrigierter Code
stability_data <- data.frame(
  samples = c("TRIM33-KO", "TRIM28-KO", "MIB1-KO", "USP28-KO"),
  mean = c(
    mean(c(data_complete[["SBNO1 end"]][["TRIM33 I"]][1, "2^(delta deltaCT)"], data_complete[["SBNO1 end"]][["TRIM33 II"]][1, "2^(delta deltaCT)"])),
    mean(c(data_complete[["SBNO1 end"]][["TRIM28 I"]][1, "2^(delta deltaCT)"], data_complete[["SBNO1 end"]][["TRIM28 II"]][1, "2^(delta deltaCT)"])),
    mean(c(data_complete[["SBNO1 end"]][["MIB1 I"]][1, "2^(delta deltaCT)"], data_complete[["SBNO1 end"]][["MIB1 II"]][1, "2^(delta deltaCT)"])),
    mean(c(data_complete[["SBNO1 end"]][["USP28 I"]][1, "2^(delta deltaCT)"], data_complete[["SBNO1 end"]][["USP28 II"]][1, "2^(delta deltaCT)"]))
  ),
  sd = c(
    sd(c(data_complete[["SBNO1 end"]][["TRIM33 I"]][1, "2^(delta deltaCT)"], data_complete[["SBNO1 end"]][["TRIM33 II"]][1, "2^(delta deltaCT)"])),
    sd(c(data_complete[["SBNO1 end"]][["TRIM28 I"]][1, "2^(delta deltaCT)"], data_complete[["SBNO1 end"]][["TRIM28 II"]][1, "2^(delta deltaCT)"])),
    sd(c(data_complete[["SBNO1 end"]][["MIB1 I"]][1, "2^(delta deltaCT)"], data_complete[["SBNO1 end"]][["MIB1 II"]][1, "2^(delta deltaCT)"])),
    sd(c(data_complete[["SBNO1 end"]][["USP28 I"]][1, "2^(delta deltaCT)"], data_complete[["SBNO1 end"]][["USP28 II"]][1, "2^(delta deltaCT)"]))
  )
)

stability_data$samples <- factor(stability_data$samples, levels = c("TRIM33-KO", "TRIM28-KO", "MIB1-KO", "USP28-KO"))


stability_single_data <- data.frame(single_samples = c("TRIM33-KO", "TRIM28-KO", "MIB1-KO", "USP28-KO", "TRIM33-KO", "TRIM28-KO", "MIB1-KO", "USP28-KO"),
                                     single_data = c(data_complete[["SBNO1 end"]][["TRIM33 I"]][1,"2^(delta deltaCT)"], 
                                                     data_complete[["SBNO1 end"]][["TRIM28 I"]][1,"2^(delta deltaCT)"],
                                                     data_complete[["SBNO1 end"]][["MIB1 I"]][1,"2^(delta deltaCT)"],
                                                     data_complete[["SBNO1 end"]][["USP28 I"]][1,"2^(delta deltaCT)"],
                                                     data_complete[["SBNO1 end"]][["TRIM33 II"]][1,"2^(delta deltaCT)"],
                                                     data_complete[["SBNO1 end"]][["TRIM28 II"]][1,"2^(delta deltaCT)"],
                                                     data_complete[["SBNO1 end"]][["MIB1 II"]][1,"2^(delta deltaCT)"],
                                                     data_complete[["SBNO1 end"]][["USP28 II"]][1,"2^(delta deltaCT)"]))

stability_single_data$single_samples <- factor(stability_single_data$single_samples, 
                                               levels = c("TRIM33-KO", "TRIM28-KO", "MIB1-KO", "USP28-KO"))


#install.packages("ggprism")
#install.packages("ggplot2")
library(ggplot2)
library(ggprism)

qPCR_stability <- ggplot()+
  geom_bar(data = stability_data, aes(x = samples, y = mean), stat = "identity", 
           fill = "khaki1", color = "goldenrod2", width = 0.6, size = 1)+
  geom_errorbar(data = stability_data, aes(x = samples, ymin = mean - sd, ymax = mean + sd), 
                color = "goldenrod2", width = 0.4, size = 0.8) +
  geom_point(data = stability_single_data, aes(x = single_samples, y = as.numeric(single_data)), 
             position = position_jitter(width = 0.2), size = 3, color = "goldenrod2", na.rm = TRUE) +
  scale_x_discrete(labels = c("TRIM33-KO", "TRIM28-KO", "MIB1-KO", "USP28-KO"))+
  #geom_text(data = qPCR_rel_data[[i]], aes(x = samples, y = target_2ddCT, label = round(target_2ddCT, 1)), vjust = -1) +
  theme_prism()+
  labs(y = expression(2^{Delta * Delta * CT}), x = "")+
  theme(axis.title.x = element_text(size = 16),
          axis.title.y = element_text(size = 16), 
          axis.text.x = element_text(size = 16),
          axis.text.y = element_text(size = 16))
  
print(qPCR_stability)

ggsave("C:/Users/sylvi/Documents/0. Arbeit/Studium/Bachelorarbeit/Abbildungen/R Plots/qPCR SBNO1 stability.svg", plot = qPCR_stability, width = 8, height = 5)

```
